### 2025-10-06 submissions/03-jpam-RR/manuscript_main.tex
new edits

\subsection{Asian Racial Identity Attrition by Generation and Family Structure}

@@

where $Y_{ist}$ represents the categorical racial identity of person $i$ in state $s$ at interview time $t$, $j$ indexes the identity categories, with "Asian only" as the reference category, $P(Y_{ist}^g = j)$ denotes the probability of person $i$ in state $s$ at time $t$ choosing identity $j$, $\mathbf{X}_{ist}^g$ represents the vector of controls that include quartic age, Asian population fraction, parent types, grandparent types, and generation dummies, $\boldsymbol{\beta}_j^g$ denotes the coefficient vector for outcome $j$ and generation $g$, and $J$ indexes the three identity categories. Finally, $\gamma_{rtj}$ represents region-time fixed effects that would control for region $\times$ year specific shocks affecting identity choice $j$, and $\varepsilon_{istj}$ is the error term.

The model specification allows the effects of anti-Asian bias and other covariates to vary across identity choices. For instance, $\beta_{1,\text{White only}}^g$ captures how anti-Asian bias affects the log-odds of choosing "White only" versus "Asian only" identity, while $\beta_{1,\text{Asian and White}}^g$ measures the bias effect on choosing "Asian and White" versus "Asian only." This framework enables analysis of how bias, sex, and parental education differentially influences various identity strategies available to individuals with Asian ancestry.

@@

The multinomial specification proves particularly appropriate for analyzing Asian American identity choices because it accounts for the distinct utility individuals may derive from different identity options. Unlike binary choice models, the multinomial framework recognizes that choosing "White only" identity represents a fundamentally different strategy than selecting "Asian and White" multiracial identification, even though both alternatives to "Asian only" may respond to anti-Asian bias. This distinction is particularly important for mixed-ancestry individuals, who may strategically choose between complete ethnic distancing (reporting "White only") versus maintaining partial ethnic connection through multiracial identification ("Asian and White").

@@

I report the results using adult samples in Figure (\ref{plot01-regression-gen-adults}). I present results estimating the main specification for all adults in panel (A) and for first- and second-generation subsamples in panels (B) and (C), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among first-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 2 percentage point decreases in Asian racial identity reporting but is statistically insignificant. Among second-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting. The adult specifications reveal additional socioeconomic influences: higher household income and years of education both positively correlate with Asian identity reporting, with each additional year of education associated with approximately 1-2 percentage point increases in the probability of reporting Asian identity.

@@

I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA adult children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults. Among endogamous Asian families, years of education does not affect children's Asian identity reporting. In contrast, among native-born second generation mixed-race adult children, higher years of education consistently show positive effects on Asian identity reporting.

@@

In this section, I discuss the results from the multinomial logit analysis. These results reveal how anti-Asian bias differentially affects the probability of choosing "Asian only," "White only," or "Asian and White" racial identification, with particularly pronounced effects among mixed-race Asian Americans. Given that the results are mainly driven by individuals with mixed ancestry, I focus the discussion on overall patterns and subsamples with mixed ancestry. The results from the multinomial logit models are in log-odds form, which are difficult to interpret directly. Therefore, I present predicted probabilities and marginal effects to facilitate interpretation.

@@

I report main results from estimating equation (\ref{eq:multinomial_logit}) in Figure \ref{fig:pp-all-gen}, showing predicted probabilities from the multinomial logit model, and in Figure \ref{fig:marginal-effects-all}, displaying the corresponding marginal effects.I find that the multinomial logit analysis reveals how anti-Asian bias differentially affects the probability of choosing ``Asian only,'' ``White only,'' or ``Asian and White'' racial identification across all generations. I observe that anti-Asian bias produces the most pronounced effects on racial identity choice. When anti-Asian bias increases from its lowest level (-0.7) to its highest level (1.3), I find that the predicted probability of ``Asian only'' identification decreases dramatically from 98\% to 48\%, representing a 50 percentage point decline. Simultaneously, I observe that ``White only'' identification increases substantially from 1\% to 43\%, while ``Asian and White'' identification shows a modest increase from 1\% to 8\%. The marginal effects confirm these patterns: a one-unit increase in anti-Asian bias decreases the probability of ``Asian only'' identification by approximately 14 percentage points while increasing ``White only'' identification by 11 percentage points.

In contrast, I find that gender and parental education produce minimal effects on racial identity choices across all generations. I observe that female respondents exhibit virtually identical probabilities of ``Asian only'' identification compared to males (91\% vs. 92\%), with minimal variation in ``White only'' (6\% vs. 5\%) and ``Asian and White'' (2\% vs. 3\%) identification. I find that parental education demonstrates similarly limited influence: college-educated fathers show negligible effects, with ``Asian only'' identification remaining stable at 92\% regardless of paternal education status, while ``White only'' and ``Asian and White'' probabilities remain virtually unchanged at 6\% and 2--3\% respectively. I observe that maternal college education produces minimal variation, with ``Asian only'' identification increasing only slightly from 91\% to 92\% when mothers hold college degrees. I find that the marginal effects confirm these modest associations, showing that both gender and parental college education alter ``Asian only'' identification by approximately 1 percentage point. These patterns demonstrate that I find anti-Asian bias drives racial identity choice variation across all generations, while demographic and family characteristics play secondary roles in shaping identity reporting decisions.

@@

I report main results from estimating equation (\ref{eq:multinomial_logit}) for second-generation subsamples by parental composition in Figures \ref{fig:pp-second-aw} and \ref{fig:pp-second-wa}, showing predicted probabilities for AW and WA families respectively. Figure \ref{fig:marginal-effects-second-parental} displays the corresponding marginal effects for both family types. I find that among second-generation Asian Americans, parental composition reveals interesting differences between Asian father-White mother (AW) and White father-Asian mother (WA) families. I observe that anti-Asian bias produces dramatically different effects across these family types. Among AW families, I find that anti-Asian bias effects are particularly pronounced: as bias increases from minimum to maximum levels (-0.7 to 1.3), ``Asian only'' identification probability decreases from 66\% to 28\%, representing a 38 percentage point decline, while ``White only'' identification increases from 3\% to 55\%. Among WA families, I observe even more dramatic patterns: ``Asian only'' identification decreases from 54\% to 18\%, while ``Asian and White'' identification increases from 40\% to 62\%. The marginal effects confirm these patterns: I estimate that a one-unit increase in anti-Asian bias decreases ``Asian only'' identification by approximately 13 percentage points among AW families and 15 percentage points among WA families, while increasing ``White only'' identification by 20 percentage points among AW families and 5 percentage points among WA families.

I find that gender and parental education produce markedly different effects between these family types. Among AW families, I observe that gender has minimal effects: female respondents exhibit virtually identical probabilities of ``Asian only'' identification compared to males (55\% vs. 59\%), with modest increases in ``Asian and White'' identification (32\% vs. 28\%). Among WA families, I find more pronounced gender differences: females show lower ``Asian only'' identification (29\% vs. 26\%) but substantially higher ``Asian and White'' identification (54\% vs. 62\%). When I examine the role of parental education on racial identity choices, I observe that among AW families, having a college-educated father decreases ``Asian only'' identification from 61\% to 53\%, while college-educated mothers increase it from 51\% to 62\%. Among WA families, I find that parental education has minimal effects on racial identity choices, with college-educated fathers and mothers producing virtually no change in identity probabilities across all categories.

I find that the marginal effects reveal how parental education operates differently across AW (Figure \ref{subfig:meaw}) and WA (Figure \ref{subfig:mewa})  family structures, providing insights into the mechanisms through which family composition shapes identity choices. Among AW families, I observe that parental education produces paradoxical effects: having a college-educated father decreases ``Asian only'' identification by approximately 8 percentage points while slightly decreasing ``White only'' identification by 2 percentage points, with the difference flowing toward ``Asian and White'' identification, which increases by 3 percentage points. I find that maternal college education among AW families generates stronger effects in the opposite direction, increasing ``Asian only'' identification by approximately 11 percentage points while decreasing both ``White only'' and ``Asian and White'' identification by 6 and 2 percentage points, respectively.

Among WA families, I observe different patterns where parental education effects are considerably smaller. I find that having a college-educated father produces minimal effects: decreasing ``Asian only'' identification by only 1 percentage point while slightly decreasing ``White only'' identification by 1 percentage point and increasing ``Asian and White'' identification by 4 percentage points. I observe that maternal college education among WA families shows similarly modest effects, increasing ``Asian only'' identification by 3 percentage points while having virtually no effect on ``White only'' identification and decreasing ``Asian and White'' identification by 1 percentage point.

I find that anti-Asian bias effects dwarf parental education influences in both family types. Among AW families, I find that a one-unit increase in anti-Asian bias decreases ``Asian only'' identification by 13 percentage points while dramatically increasing ``White only'' identification by 20 percentage points, with minimal effects on ``Asian and White'' identification. Among WA families, I observe that the same bias increase decreases ``Asian only'' identification by 15 percentage points but increases ``Asian and White'' identification by 8 percentage points and ``White only'' identification by only 5 percentage points. These patterns suggest that I find AW families use White identification as the primary response to bias, while WA families gravitate toward multiracial identification, with parental education serving as a moderating rather than determining factor in these strategic identity choices.

@@

I observe that anti-Asian bias produces dramatically different effects across grandparent combinations. Among those with one Asian grandparent, I find a small response to bias: as bias increases from minimum to maximum levels (-0.7 to 1.3), ``Asian only'' identification decreases modestly from 11\% to 3\%, while ``White only'' identification decreases from 55\% to 49\%, and ``Asian and White'' increases from 34\% to 48\%. Those with two Asian grandparents show intermediate patterns: ``Asian only'' identification decreases from 48\% to 13\%, ``White only'' identification increases from 21\% to 49\%, and ``Asian and White'' identification shifts from 31\% to 38\%. Among those with three Asian grandparents, I find relatively stable effects of bias on racial identity. ``Asian only'' identification remain approximately the same at around 95\% until bias increases from 1 to 1.3 when it decreases by 20 percentage points. The same pattern persists for ``White only'' identification increases from 0\% to 21\% when bias increases from 1 to 1.3, and ``Asian and White'' identification remains constant at 4-6\% regardless of the level of bias.

I find that gender and parental education effects vary systematically across grandparent configurations. Among those with one Asian grandparent, I observe minimal gender effects: females show virtually identical patterns to males across all identity categories (6\% vs. 7\% for ``Asian only,'' 50\% vs. 56\% for ``White only,'' and 44\% vs. 37\% for ``Asian and White''). Those with two Asian grandparents show the most pronounced gender effects: females demonstrate lower ``Asian only'' identification (19\% vs. 22\%) and higher ``White only'' identification (43\% vs. 39\%). Among those with three Asian grandparents, I find modest gender differences: females exhibit slightly lower ``Asian only'' identification (93\% vs. 95\%) and higher ``Asian and White'' identification (7\% vs. 5\%).

I find that parental education operates differently across ancestral configurations. Among those with one Asian grandparent, I observe that paternal college education decreases ``Asian only'' identification from 8\% to 5\% while increasing ``Asian and White'' identification from 38\% to 43\%. Maternal college education shows similar modest effects. Among those with two Asian grandparents, I observe the strongest parental education effects: maternal college education decreases ``Asian only'' identification from 18\% to 23\% while decreasing ``Asian and White'' identification from 45\% to 34\%. Among those with three Asian grandparents, I find that parental education produces stronger effects: paternal college education decreases ``Asian only'' identification from 97\% to 89\% while increasing ``Asian and White'' identification from 3\% to 10\%.

The marginal effects reveal that I find anti-Asian bias produces the strongest effects among those with three Asian grandparents, where a one-unit increase in bias decreases ``Asian only'' identification by approximately 2 percentage points. Among those with one or two Asian grandparents, I observe smaller and often statistically insignificant bias effects. These patterns demonstrate that I find greater Asian ancestry amplifies responsiveness to social bias, while extensive ancestral dilution reduces the salience of anti-Asian attitudes in identity choice decisions.

@@

The multinomial logit analysis demonstrates that anti-Asian bias fundamentally reshapes racial identity. When bias increases from minimum to maximum levels, the probability of ``Asian only'' identification decreases dramatically from 9m\% to 48\%, while ``White only'' identification increases from 1\% to 43\%. These strategic identity choices are most pronounced among mixed-race families, where high bias environments drive substantial shifts toward White identification among Asian father-White mother families and toward multiracial identification among White father-Asian mother families.

I also find that anti-Asian bias positively correlates with interracial marriage and shows no correlation with migration decisions, suggesting that identity switching rather than geographic or partnership selection drives the observed patterns.

These results are important due to consequences for correct Asian American and minority enumeration, integration patterns, and social mobility. They indicate anti-Asian bias could significantly affect how economists estimate racial gaps. Most race and ethnicity research relies on self-reported racial and ethnic identity measures. Since anti-Asian bias negatively correlates with Asian racial identity reporting, characteristics of those avoiding Asian racial identification could produce important consequences. For example, if individuals whose identities are most likely affected by bias represent the most educated, then racial gaps will be overestimated in the most biased states. Furthermore, identity decisions likely profoundly affect people's choices, investments, and well-being.

>>>>

\subsection{Asian Racial Identity Attrition by Generation and Family Type}

@@

where $Y_{ist}$ represents the categorical racial identity of person $i$ in state $s$ at interview time $t$, $j$ indexes the identity categories, with ``Asian only'' as the reference category, $P(Y_{ist}^g = j)$ denotes the probability of person $i$ in state $s$ at time $t$ choosing identity $j$, $\mathbf{X}_{ist}^g$ represents the vector of controls that include quartic age, Asian population fraction, parent types, grandparent types, and generation dummies, $\boldsymbol{\beta}_j^g$ denotes the coefficient vector for outcome $j$ and generation $g$, and $J$ indexes the three identity categories. Finally, $\gamma_{rtj}$ represents region-time fixed effects that would control for region $\times$ year specific shocks affecting identity choice $j$, and $\varepsilon_{istj}$ is the error term.

The model specification allows the effects of anti-Asian bias and other covariates to vary across identity choices. For instance, $\beta_{1,\text{White only}}^g$ captures how anti-Asian bias affects the log-odds of choosing ``White only'' versus ``Asian only'' identity, while $\beta_{1,\text{Asian and White}}^g$ measures the bias effect on choosing ``Asian and White'' versus "Asian only." This framework enables analysis of how bias, sex, and parental education differentially influences various identity strategies available to individuals with Asian ancestry.

@@

The multinomial specification proves particularly appropriate for analyzing Asian American identity choices because it accounts for the distinct utility individuals may derive from different identity options. Unlike binary choice models, the multinomial framework recognizes that choosing ``White only'' identity represents a fundamentally different strategy than selecting ``Asian and White'' multiracial identification, even though both alternatives to ``Asian only'' may respond to anti-Asian bias. This distinction is particularly important for mixed-ancestry individuals, who may strategically choose between complete ethnic distancing (reporting ``White only'') versus maintaining partial ethnic connection through multiracial identification (``Asian and White'').

@@

I report the results using adult samples in Figure (\ref{plot01-regression-gen-adults}).\footnote{As I note in the data section, for adults with Asian ancestry, I could only observe the places of birth of the person and their parents. Since I cannot observe the places of birth of grandparents, I could only analyze the effects on first- and second-generation individuals with Asian ancestry.} I present results estimating the main specification for all adults in panel (A) and for first- and second-generation subsamples in panels (B) and (C), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among first-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 2 percentage point decreases in Asian racial identity reporting but is statistically insignificant. Among second-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting. The adult specifications reveal additional socioeconomic influences: higher household income and years of education both positively correlate with Asian identity reporting, with each additional year of education associated with approximately 1-2 percentage point increases in the probability of reporting Asian identity.

@@

I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA adult children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults. Among endogamous Asian families, years of education does not affect children's Asian identity reporting. In contrast, among native-born second generation mixed-race adult children, higher years of education consistently show positive effects on Asian identity reporting. Therefore, more educated individuals with Asian ancestry are more likely to keep their Asian racial identity. Consequently, if more educated Asian immigrants keep their racial identity while those that are less educated are more likely to attrit, then Asian individuals may appear to be doing better and they are assimilating faster than other immigrant groups.

@@

In this section, I discuss the results from the multinomial logit analysis. These results reveal how anti-Asian bias differentially affects the probability of choosing ``Asian only,`' ``White only,'' or ``Asian and White'' racial identity, with particularly pronounced effects among mixed-race Asian Americans. Given that the results are mainly driven by individuals with mixed ancestry, I focus the discussion on overall patterns and subsamples with mixed ancestry. The results from the multinomial logit models are in log-odds form, which are difficult to interpret directly. Therefore, I present predicted probabilities and marginal effects to facilitate interpretation.

@@

I report main results from estimating equation (\ref{eq:multinomial_logit}) in Figure \ref{fig:pp-all-gen}, showing predicted probabilities from the multinomial logit model, and in Figure \ref{fig:marginal-effects-all}, displaying the corresponding marginal effects. I find that the multinomial logit analysis reveals how anti-Asian bias differentially affects the probability of choosing ``Asian only,'' ``White only,'' or ``Asian and White'' racial identities across all generations. I observe that anti-Asian bias produces the most pronounced effects on racial identity choice. When anti-Asian bias increases from its lowest level (-0.7) to its highest level (1.3), I find that the predicted probability of reporting ``Asian only'' identity decreases dramatically from 98\% to 48\%, representing a 50 percentage point decline. Simultaneously, I observe that reporting ``White only'' identity increases substantially from 1\% to 43\%, while reporting ``Asian and White'' identity shows a modest increase from 1\% to 8\%. The marginal effects confirm these patterns: a one-unit increase in anti-Asian bias decreases the probability of reporting ``Asian only'' identity by approximately 14 percentage points while increasing reporting ``White only'' identity by 11 percentage points.

In contrast, I find that gender and parental education produce minimal effects on racial identity choices across all generations. I observe that female respondents exhibit virtually identical probabilities of reporting ``Asian only'' identity compared to males (91\% vs. 92\%), with minimal variation in reporting ``White only'' (6\% vs. 5\%) and ``Asian and White'' (2\% vs. 3\%) identities. I find that parental education demonstrates similarly limited influence: college-educated fathers show negligible effects, with ``Asian only'' identity remaining stable at 92\% regardless of paternal education status, while ``White only'' and ``Asian and White'' probabilities remain virtually unchanged at 6\% and 2--3\% respectively. I observe that maternal college education produces minimal variation, with ``Asian only'' identity increasing only slightly from 91\% to 92\% when mothers hold college degrees. I find that the marginal effects confirm these modest associations, showing that both gender and parental college education alter ``Asian only'' identification by approximately 1 percentage point. These patterns demonstrate that I find anti-Asian bias drives racial identity choice variation across all generations, while demographic and family characteristics play secondary roles in shaping identity reporting decisions.

@@

I report main results from estimating equation (\ref{eq:multinomial_logit}) for second-generation subsamples by parental composition in Figures \ref{fig:pp-second-aw} and \ref{fig:pp-second-wa}, showing predicted probabilities for AW and WA families respectively. Figure \ref{fig:marginal-effects-second-parental} displays the corresponding marginal effects for both family types. I find that among second-generation Asian Americans, parental composition reveals interesting differences between Asian father-White mother (AW) and White father-Asian mother (WA) families. I observe that anti-Asian bias produces dramatically different effects across these family types. Among AW families, I find that anti-Asian bias effects are particularly pronounced: as bias increases from minimum to maximum levels (-0.7 to 1.3), the probability of reporting ``Asian only'' identity decreases from 66\% to 28\%, representing a 38 percentage point decline, while the probability of reporting ``White only'' identity increases from 3\% to 55\%. Among WA families, I observe even larger patterns: the probability of reporting ``Asian only'' identity decreases from 54\% to 18\%, while the probability of reporting ``Asian and White'' identity increases from 40\% to 62\%. The marginal effects confirm these patterns: I estimate that a one-unit increase in anti-Asian bias decreases the probability of reporting ``Asian only'' identity by approximately 13 percentage points among AW families and 15 percentage points among WA families, while increasing the probability of reporting ``White only'' identity by 20 percentage points among AW families and 5 percentage points among WA families.

I find that gender and parental education produce markedly different effects between these family types. Among AW families, I observe that gender has minimal effects: female respondents exhibit virtually identical probabilities of reporting ``Asian only'' identity compared to males (55\% vs. 59\%), with modest increases in the probability of reporting ``Asian and White'' identity (32\% vs. 28\%). Among WA families, I find more pronounced gender differences: females show lower probability of reporting ``Asian only'' identity (29\% vs. 26\%) but substantially lower probability of reporting ``Asian and White'' identity (62\% vs. 54\%). When I examine the role of parental education on racial identity choices, I observe that among AW families, having a college-educated father decreases the probability of reporting ``Asian only'' identity from 61\% to 53\%, while college-educated mothers increase it from 51\% to 62\%. Among WA families, I find that parental education has minimal effects on racial identity choices, with college-educated fathers and mothers producing virtually no change in identity probabilities across all categories.

I find that the marginal effects reveal how parental education operates differently across AW (Figure \ref{subfig:meaw}) and WA (Figure \ref{subfig:mewa})  family structures, providing insights into the mechanisms through which family composition shapes identity choices. Among AW families, I observe that parental education produces paradoxical effects: having a college-educated father decreases the probability of reporting ``Asian only'' identity by approximately 8 percentage points while slightly increasing the probability of reporting ``White only'' identity by 2 percentage points, with the difference flowing toward the probability of reporting ``Asian and White'' identity, which increases by 3 percentage points. I find that maternal college education among AW families generates stronger effects in the opposite direction, increasing the probability of reporting ``Asian only'' identity by approximately 11 percentage points while decreasing the probability of reporting ``White only'' identity by 11 percentage points.

Among WA families, I observe different patterns where parental education effects are considerably smaller. I find that having a college-educated father produces minimal effects: decreasing the probability of reporting ``Asian only'' identity by only 1 percentage point while slightly decreasing the probability of reporting ``White only'' identity by 1 percentage point and increasing the probability of reporting ``Asian and White'' identity by 4 percentage points. I observe that maternal college education among WA families shows similarly modest effects, increasing the probability of reporting ``Asian only'' identity by 3 percentage points while having virtually no effect on the probability of reporting ``White only'' identity and decreasing the probability of reporting ``Asian and White'' identity by 1 percentage point.

I find that anti-Asian bias effects dwarf parental education influences in both family types. Among AW families, I find that a one-unit increase in anti-Asian bias decreases the probability of reporting ``Asian only'' identity by 13 percentage points while dramatically increasing the probability of reporting ``White only'' identity by 20 percentage points, and small decreasing effects on the probability of reporting ``Asian and White'' identity. Among WA families, I observe that the same bias increase decreases the probability of reporting ``Asian only'' identity by 15 percentage points but increases the probability of reporting ``Asian and White'' identity by 8 percentage points and the probability of reporting ``White only'' identity by only 6 percentage points. These patterns suggest that I find AW families use White identification as the primary response to bias, while WA families gravitate toward multiracial identification, with parental education serving as a moderating rather than determining factor in these strategic identity choices.

I report the results using adult samples in Figure (\ref{fig:pp-secondgen-adults-aw-wa}) showing predicted probabilities for adult children of AW and WA parents. Among AW families (Panel a), I find that as anti-Asian bias increases from minimum to maximum levels (-0.7 to 1.3) the probability of reporting: ``White only'' identity increases from 12\% to 39\%, ``Asian and White'' decreases from 46\% to 16\%, and ``Asian only'' is basically unchanged. Among WA families (Panel a), I find that as anti-Asian bias increases from minimum to maximum levels (-0.7 to 1.3) the probability of reporting: ``White only'' identity increases from 27\% to 38\%, ``Asian and White'' increases from 25\% to 40\%, and ``Asian only'' decreases from 47\% to 22\%. For both adult children of AW and WA families gender does not seem to play an effect in determining Asian identity choices.

@@

I observe that anti-Asian bias produces dramatically different effects across grandparent combinations. Among those with one Asian grandparent, I find a small response to bias. As bias increases from minimum to maximum levels (-0.7 to 1.3) the probability of reporting: ``Asian only'' identity decreases from 11\% to 3\%, the probability of reporting ``White only'' identity decreases from 55\% to 49\%, and the probability of reporting ``Asian and White'' identity increases from 34\% to 48\%. Among those with two Asian grandparents, the probability of reporting: ``Asian only'' identity decreases from 48\% to 13\%, the probability of reporting ``White only'' identity increases from 21\% to 49\%, and the probability of reporting ``Asian and White'' identity shifts from 31\% to 38\%. Among those with three Asian grandparents, I find relatively stable effects of bias on racial identity. The probability of reporting ``Asian only'' identity remains approximately the same at around 95\% until bias increases from 1 to 1.3 when it decreases by 20 percentage points. The same pattern persists for the probability of reporting ``White only'' identity which increases from 0\% to 21\% when bias increases from 1 to 1.3, and the probability of reporting ``Asian and White'' identity remains constant at 4-6\% regardless of the level of bias.

I find that gender and parental education effects vary systematically across grandparent types. Among those with one Asian grandparent, I observe minimal gender effects. Females show virtually identical patterns to males across all identity categories (7\% male vs. 6\% female for the probability of reporting ``Asian only'' identity, 56\% vs. 50\% for the probability of reporting ``White only'' identity, and 37\% vs. 44\% for the probability of reporting ``Asian and White'' identity). Those with two Asian grandparents show the most pronounced gender effects. Females report lower probability of reporting ``Asian only'' identity vs males (22\% vs. 19\%) and higher probability of reporting ``White only'' identity (39\% vs. 43\%). Among those with three Asian grandparents, I find modest gender differences: females report slightly lower probability of reporting ``Asian only'' identity (95\% vs. 93\%) and higher probability of reporting ``Asian and White'' identity (5\% vs. 7\%).

I find that parental education operates differently across ancestral types. Among those with one Asian grandparent, I observe that paternal college education decreases the probability of reporting ``Asian only'' identity from 8\% to 5\% while increasing the probability of reporting ``Asian and White'' identity from 38\% to 43\%. Maternal college education shows similar modest effects. Among those with two Asian grandparents, I observe the strongest parental education effects: maternal college education decreases the probability of reporting ``Asian only'' identity from 18\% to 23\% while decreasing the probability of reporting ``Asian and White'' identity from 45\% to 34\%. Among those with three Asian grandparents, I find that parental education produces stronger effects: paternal college education decreases the probability of reporting ``Asian only'' identity from 97\% to 89\% while increasing the probability of reporting ``Asian and White'' identity from 3\% to 10\%.

The marginal effects reveal that I find anti-Asian bias produces the strongest effects among those with three Asian grandparents, where a one-unit increase in bias decreases the probability of reporting ``Asian only'' identity by approximately 2 percentage points. Among those with one or two Asian grandparents, I observe smaller and often statistically insignificant bias effects. These patterns demonstrate that I find greater Asian ancestry amplifies responsiveness to social bias, while extensive ancestral dilution reduces the salience of anti-Asian attitudes in identity choice decisions.

@@

Using multinomial logit analysis, I show that anti-Asian bias fundamentally reshapes racial identity. When bias increases from minimum to maximum levels, the probability of reporting ``Asian only'' identity decreases dramatically from 9m\% to 48\%, while ``White only'' identity increases from 1\% to 43\%. These strategic identity choices are most pronounced among mixed-race families, where high bias environments drive substantial shifts toward White identification among Asian father-White mother families and toward multiracial identification among White father-Asian mother families.

These results are important due to consequences for correct Asian American and minority enumeration, assimilation patterns, and social mobility. The results I find indicate that anti-Asian bias could significantly affect how economists and social scientists estimate racial gaps. Most race and ethnicity research relies on self-reported racial and ethnic identity measures. Since anti-Asian bias negatively correlates with Asian racial identity reporting, characteristics of those avoiding Asian racial identification could lead to important consequences. For example, if individuals whose identities are most likely affected by bias represent the most educated, then racial gaps will be overestimated in the most biased states. Furthermore, identity decisions likely profoundly affect people's choices, investments, and well-being.

### 2025-10-06 submissions/03-jpam-RR/manuscript_title_etc.tex
new edits

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points across all generations. The effects vary by generation and family structure: bias decreases Asian identification by 5 percentage points among first-generation immigrants (statistically insignificant), 8 percentage points among second-generation, and 8 percentage points among third-generation Asian Americans. Mixed-race families show the strongest responses, with bias decreasing Asian identification by 15 percentage points among children of Asian fathers and White mothers, and 10 percentage points among children of White fathers and Asian mothers. Using multinomial analyses, I find that high bias environments drive substantial shifts from ``Asian only'' to ``White only'' identification, with probabilities changing by up to 50 percentage points. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
\PAPERJEL}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points across all generations. The effects vary by generation and family structure: bias decreases Asian identification by 5 percentage points among first-generation immigrants (statistically insignificant), 8 percentage points among second-generation, and 8 percentage points among third-generation Asian Americans. Mixed-race families show the strongest responses, with bias decreasing Asian identification by 15 percentage points among children of Asian fathers and White mothers, and 10 percentage points among children of White fathers and Asian mothers. Using multinomial logit regression, I find that high bias environments drive substantial shifts from ``Asian only'' to ``White only'' identification, with probabilities changing by up to 50 percentage points. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
\PAPERJEL}
